Lyman-$\alpha$ photons through rotating outflows

### 2018-11-03 paper/paper.tex
last revision

\begin{figure*}
\centering
    \includegraphics[width=0.48\textwidth]{doppler_shift_logtau6_theta90}
    \includegraphics[width=0.48\textwidth]{doppler_shift_logtau6_theta0}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed perpendicular/paralell to the
      rotation axis}.  
    Here we fix $\tauh=10^6$. 
    The six panels on the left correspond to $\theta=90^\circ$ and the
    panels on the right to $\theta=0^{\circ}$
    We vary \vrot increasing from left to right and \vout increasing
    from top to bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifying the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of
    only outflows, but also a Doppler shift from the rotational
    velocity (thick and dark line).  
    \label{fig:doppler_shift}}
\end{figure*}

@@

\cite{Garavito14} presented an analytical model that
accounts for the effects of pure rotation on the
\lya line morphology. 
The basic assumption of the model is that each differential surface
element on the sphere Doppler shifts the photons that it emits.
In this paper we introduce this ansatz by post-processing the results
of the outflows simulations without rotation.
The frequency of each photon is Doppler shifted as follows

@@

In this paper we explore, for the first time in the literature,
the results of a model for the emergent \lya line from rotating
outflows. 
We the a semi-analytic model first presented by \cite{Garavito14}
to capture the main effects of rotation and confront it against
results from Monte-Carlo radiative transfer simulations. 
The semi-analytic model only takes into account the Doppler shift computed
as product of quantities at the surface of last scattering, namely
$\vec{v}_{\rm rot}\cdot \hatk$, where $\vec{v}_{\rm rot}$ is the
velocity due to rotation and \hatk is the direction of the photon's
propagation.

@@

To summarize, our works shows that the Doppler Shift offers an
easy-to-implement approximation to explore such influence into already
existing radiative transfer simulation simulations that include
outflows, providing a versatile tool to interpret current and future \lya
kinematics maps  \citep[e.g][]{2018MNRAS.473.3907A}.

>>>>

\begin{figure*}
\centering
    \includegraphics[width=0.48\textwidth]{doppler_shift_logtau6_theta90}
    \includegraphics[width=0.48\textwidth]{doppler_shift_logtau6_theta0}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed perpendicular/paralell to the
      rotation axis}.  
    Here we fix $\tauh=10^6$. 
    The six panels on the left correspond to $\theta=90^\circ$ and the
    panels on the right to $\theta=0^{\circ}$
    We vary \vrot increasing from left to right and \vout increasing
    from top to bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to CLARA's results including both
    outflows and rotation.
    The thick gray line shows the results of modifying the pure outflow
    solution (thin black line) by the Doppler shift presented in Equation \ref{eq:shift_x} using the respective \vrot. 
    \label{fig:doppler_shift}}
\end{figure*}

@@

\cite{Garavito14} presented an analytical model that
accounts for the effects of pure rotation on the
\lya line morphology. 
The basic assumption of the model is that each differential surface
element on the sphere Doppler shifts (DS) the photons that it emits.
In this paper we introduce this ansatz by post-processing the results
of the outflows simulations without rotation.
The frequency of each photon is Doppler shifted as follows

@@

In this paper we explore, for the first time in the literature,
the results of a model for the emergent \lya line from rotating
outflows. 
We use a semi-analytic model first presented by \cite{Garavito14}
to capture the main effects of rotation and confront it against
results from Monte-Carlo radiative transfer simulations. 
The semi-analytic model only takes into account the Doppler shift computed
as product of quantities at the surface of last scattering, namely
$\vec{v}_{\rm rot}\cdot \hatk$, where $\vec{v}_{\rm rot}$ is the
velocity due to rotation and \hatk is the direction of the photon's
propagation.

@@

To summarize, our works shows that the Doppler Shift offers an
easy-to-implement approximation to explore such influence into already
existing radiative transfer simulations that include
outflows, providing a versatile tool to interpret current and future \lya
kinematics maps \citep[e.g][]{2018MNRAS.473.3907A,Erb18}.
